TITLE

### 2021-02-26 outputs/Paper.Rmd
diagram update

## Descriptive Analysis
```{r read_data, include=FALSE}

setwd("~/Downloads/Git/groupproject-")

@@

@@

```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=10, fig.height=4}

@@

```{r employee, fig.cap = "Empoyee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}
cxc <- 
  simulated_data%>%
  ggplot(aes(x = simulated_data$Q8 ,fill = type)) +
  geom_bar(width = 0.7,position = "dodge") + 
  coord_polar()+
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
  labs(title = "Almost 0 restaurant has more than 30 employees in control group",x="", y="Count") +
  theme_minimal()

>>>>

## Descriptive Analysis
```{r read_data, include=FALSE}
setwd("~/Downloads/Git/groupproject-")

@@

```{r salary distribution, echo=FALSE}
sd1<-
  ggplot(simulated_data, aes(x = simulated_data$Q9, fill=type)) +
  geom_histogram(position = "dodge", bins = 30,binwidth = 0.5) +
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
  labs(title="The Salary Distributions was higher for Teatment Group", x="Salary", y="Number of employee")+
  geom_density()
```

@@

```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=7, fig.height=15}

@@

```{r employee, fig.cap = "Employee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}
cxc <- 
  simulated_data%>%
  ggplot(aes(x = simulated_data$Q8 ,fill = type)) +
  geom_bar(width = 0.7,position = "dodge") + 
  coord_polar()+
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
  labs(title = "Almost 0 restaurant has more than 30 employees in control group",x="", y="Count") +
  theme_minimal()
